---
title: "What if you drop that? Developmental changes in curiosity about physical interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf George (kachergis@stanford.edu)} \\ Department of Psychology, Stanford University \\ Madison, WI 53706 USA
    \AND {\large \bf Judith Fan (SDJ@Macc.Wisc.Edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA}

abstract: >
     Curiosity is a fundamental driver of human behavior, and yet because of its open-ended nature 
     and the wide variety of behaviors it inspires in different contexts, it is remarkably difficult 
     to study in a laboratory context. A promising approach to developing and testing theories of 
     curiosity is to instantiate them in artificial agents that are able to act and explore in a 
     simulated environment, and then compare the behavior of these agents to humans exploring the 
     same stimuli. Here we propose a new experimental paradigm for examining children's--and curious
     AI agents'--curiosity about objects' physical interactions, using a task that is both open-ended
     enough to allow room for curiosity, but also constrained enough to make detailed behavioral 
     comparisons. We children's choices (N=XX; 2-6 years of age) to those of adults (N=XX), and find
     systematic preference for drops affording particular relations (e.g., containment)
    
keywords: >
    curiosity; novel objects; object interactions; intuitive physics
    
output: cogsci2016::cogsci_paper
#    includes:
#      in_header: preamble.tex
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
library(apa) # for generating APA-style text to report statistical tests
library(ggpubr)
require(gridExtra)
```

```{r, load-data}
# preprocessed in analysis/exp2_analysis.Rmd
load(file=here("paper/processed_data.RData")) 

Nch = length(unique(child_long$ID)) # 62
Nad = length(unique(adult_long$ResponseId)) # 35

age <- child_long %>% distinct(ID, Age) %>% group_by(Age) %>%
  summarise(Age = mean(Age), N= n())
```

# Introduction 

<!-- Curiosity is important... end with core question about what gives rise to curiosity. -->
Curiosity is a hallmark aspect of human intelligence. 
From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences. 
However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015]. 
Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.

The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks. 

Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976]. 
Recent studies have provided empirical support for this basic idea: XX-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.  
Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curiosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.

Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory. 
However, the measures used in this literature have typically been coarse-grained with respect to infant's and children's physical knowledge, and thus do not specify or constrain which events might moderately discrepant from this knowledge. 
For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015; @Baillargeon2007). 
Other work that has investigated exploratory behavior in children have used more granular measures, such as counting the number of functions discovered while playing with novel and complex toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014]. 
Moreover, these studies have yet to directly constrain theories that predict which functions children will discover, and in what sequence. 
What both of the standard looking-time and toy-exploration measures fail to capture when characterizing children's curiosity are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009; @gureckis2012self]. 
To address these limitations, we developed a novel physical exploration task in which children, adults, or AI agents choose which series of physical experiments to perform and observe the results of each in real time. 

<!-- High-level statement of our approach -->
In sum, this paper presents a unified paradigm for advancing theories of curiosity and its role in guiding the development of knowledge about the physical world. 
We present: (1) a computational theory of intrinsic motivation instantiated in an artificial reinforcement-learning agent that explores a simulated 3D environment; (2) a novel dataset that measures children's actions in a novel physical exploration task; and (3) quantitative comparisons between the actions taken by the artificial agent and children on the same set of tasks. 
Overall, our approach of coordinating the development of task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of how curiosity guides cognitive development.

<!-- presents learners (children or the agent) with a set of objects from which they can select one to drop in a bin containing a set of target objects, with the potential to create one or more collisions during the drop. -->

<!-- What we've learned from prior theoretical work, and how it falls short -->

<!-- A limitation of past theories of curiosity is that they are large part verbal descriptions, without formal, testable, mechanisms. -->
<!-- An exception to this: @Schmidhuber2010 and @Oudeyer2013 --similar but different, and critically not evaluated against same children's behavior in the same situations -->

<!-- What we've learned from prior behavioral work, and how our approach is different -->

<!-- Looking time people: @Baillargeon2007 and other studies of infants' surprisal at physical events (occlusion, containment,  -->
<!-- Ullman -- not about curiosity, but about intuitive physics learning from observation in simplified 2D domains (e.g., colliding hockey pucks)  -->


<!-- Highlight main contributions of the paper -->

<!-- One rich domain that young children are in the midst of learning about is the properties and affordances of physical objects.  -->
<!-- A study of 9- to 16-month-olds found that infants' violation of expectations about a novel toy's hidden properties (e.g., making a sound) drives them to explore similar toys for longer [@Baldwin1993]. -->

## Computational Models of Curiosity

Building on prior work that showed deep neural networks are capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], we use and extend a deep RL architecture for constructing intrinsically-motivated artificial agents introduced in @Haber2018learning.
This agent's behavior is driven by two interacting neural networks: a *world-model* and a *self-model*, which are trained simultaneously. 
The problem of the world-model is to predict the consequences of the agent's actions, through estimation of either the forward or inverse dynamics. 
The self-model attempts to learn to predict the errors of the world-model. 
The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will adversarially challenge the state of its world-model.

# Experiment 1: Adults

## Method

### Participants
Participants were `r Nad` adults recruited online via Amazon Mechanical Turk.


### Materials

## Results

```{r adult-agg}
adult_trial_agg <- adult_long %>% group_by(drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
```



# Experiment 2: Children

## Method

### Participants
Participants were `r Nch` children recruited online via XX.
Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.

### Materials

Stimuli were 3D-printed plastic objects produced using Blender 3D-modeling software. 
The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, and triangular prism.
The printed objects were all yellow, rigid plastic material and designed to fit comfortably in a child's hand (dimension range: 3.8-10.1 cm). 


```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Set of 3D objects used for dropping and as targets. [REPLACE]"}
img <- png::readPNG("figs/drop_sets.png")
grid::grid.raster(img)
```

### Procedure

After the parent provided informed consent, children were assigned to Order 1 or Order 2. Participants were assigned to condition in counterbalanced order.
We introduced children to a set of 3D-printed toy objects ("blocks"). 

An example trial is illustrated in Figure 2.

Based on piloting, we estimated the activity would would only require X minutes to complete. 
In both conditions, a video camera was used to record the play session from an angle above the bin, to show child's block selection and drop location as well as child's completed tower. 
After child notified the researcher that they were finished building their tower, the session was completed.

```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial in which the participant chose to drop the pyramid on the pentagonal prism. [REPLACE]"}
img <- png::readPNG("figs/DropTaskFigure.png")
grid::grid.raster(img)
```


## Results

```{r child-data-agg}
child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

ch_ad_cor <- cor.test(child_trial_agg$chose_target, adult_trial_agg$chose_target)

trial_tab <- child_trial_agg %>% select(-n) %>% 
  bind_cols(adult_target_choice = adult_trial_agg$chose_target) %>% 
  rename(child_target_choice = chose_target) 
```

We first examine children's choice of drop objects and target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 

Were children's drop choices consistent with adults'?
Correlation between children's individual proportion of "missed" targets and their age (`r cor_apa(ch_ad_cor, format="rmarkdown", print=F)`).
Table 2 shows a summary of participants' choice of target objects per set.

<!-- Finally, we examine a more lenient analysis children's choice of target location (i.e., the identity of the closest target), regardless of whether there was a collision of drop and target objects. -->
<!-- Chi-square tests of children's target collisions once more found that ... -->
<!-- Table 3 shows a summary of participants' choice of target locations per set. -->

<!-- In summary, children showed some consistent preferences in their choice of objects to drop from each set, but no systematic preference for targeting particular objects. -->
<!-- We now investigate whether there were interactions of drop objects and targets that children found particularly appealing. [ToDo: big chisq test?] -->

<!-- Finally, we analyze how exploratory children were in their responses: across the 12 trials, what proportion of the 9 available objects did each child utilize as drop objects? What proportion of the objects were targeted? -->


```{r drop-choice, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
drop_choice_plot <- function(dat, ymax=.66, shapes_vec) {
  ch_cond <- dat %>% 
    group_by(StimSet, DropChoice) %>%
    summarise(n = n()) %>%
    mutate(freq = n / sum(n)) 

  ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
  ch_cond$DropChoice <- factor(ch_cond$DropChoice, levels=shapes_vec)
  fig_drop <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
    geom_point(alpha=.8) +
    scale_shape_manual(values=10:19) +
    #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
    xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,ymax) + 
    langcog::scale_fill_solarized() + ggthemes::theme_few() + 
    geom_hline(yintercept=.33, lty='dashed') + labs(shape="Object", color="Object")
  return(fig_drop)
}

#fig_drop <- drop_choice_plot(hum, shapes)
```



Figure 4 shows participants' mean proportion of unique objects dropped as a function of age.
Children of all ages sampled approximately equal proportions of the objects for dropping--roughly 70%, which is close to the 75% that would be expected if they were selected by chance (9 unique object occurring across 12 trials).

```{r unique-drop-objects, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion of unique objects selected by participants. Error bars show boostrapped 95\\% confidence intervals.", eval=F}
# 12 trials, 9 objects; random selection would be 9/12 = 75%...
uniq_s <- hum %>% group_by(SID, Age_Group) %>%
  summarise(DropObjs = n_distinct(DropChoice), N=n(), prop=DropObjs/N) 

uniq <- uniq_s %>% group_by(Age_Group) %>%
  tidyboot_mean(prop) 
  
ggplot(uniq, aes(x=Age_Group, y=mean)) + geom_point() +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Age (years)") + ylab("Unique Objects Chosen") + ylim(0,1) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  geom_hline(yintercept=.75, lty='dashed')
```




# Discussion 



# Acknowledgements

This work was funded by HAI seed grant #. 
We thank X and Y for helpful comments.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
