---
#title: "Modeling children's intrinsically-motivated curiosity about object interactions"
#title: "Drop it like it's hot: Modeling children's curiosity about physical interactions"
#title: "A drop in the bucket: Modeling children's curiosity about physical interactions"
title: "What if you drop that? Modeling children's curiosity about physical interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

abstract: >
    Although the question of what inspires a child's curiosity is difficult to determine,
    it's generally agreed that curiosity indicates awareness of a knowledge gap that the 
    learner is interested in filling. A promising approach to teasing apart 
    
keywords: >
    curiosity; novel objects; object interactions; intuitive physics
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
```

```{r, load-data}
raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T, stringsAsFactors=F)
hum = subset(raw, Exclude!="Y")

hum = hum[-which(hum$StimSet=="bc" & hum$DropChoice=="bowl and dumbbell"),] # chose two - exclude

s_tr <- hum %>% group_by(SID, Age_Group) %>% summarise(max=max(Trial)) %>% arrange(max)
age = table(s_tr$Age_Group)
```

# Introduction 


Within the first two years of life, human infants develop a remarkable suite of exploratory behaviors — they begin to direct their own movement through their environ- ment, they can shift their attention to events they find most interesting, and they interact with objects in complex, creative ways [2, 6, 8, 9, 23]. This ability to playfully explore and (re)structure their environment sets infants apart from even the most advanced robots today, which must be taught what to do in every scenario. The goal of this proposal is to develop computationally pre- cise models of exploration and learning that mirror the trajectory of human infant development. Our ongoing strategy is to combine approaches from artificial intelligence, computational cognitive science, and developmental psychology.

the gap: major outstanding issue in the research on curiosity and exploratory play is the functional form of the intrinsic motivation

gold standard would be direct comparison of human and AI agents, but human behavior is so wide-ranging

we propose a new paradigm that enables 

paragraph 


Whence intrinsically-motivated curiosity?
Novelty, opportunity for learning, etc.

Intuitive physics, play..

Best way to test is to create models instantiating different curiosity policies and then compare model and human behavior.

## Model subsection first

- or joint paradigm section
- developmental data collection
- model r

- simple statistical test (per drop / target set): 
chisq.test 
Observed vs Expected

# Experiment

## Method

### Participants
Participants were `r length(unique(raw$SID))` children recruited from the Children's Discovery Museum of San Jose and Bing Nursery School.
Exclusions were made based on...
After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds. 

### Materials

```{r object-sets}
shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism")

a = c("pyramid", "torus", "trig prism")
b = c("cone", "octahedron", "pipe")
c = c("bowl", "dumbbell", "pentagon")
```

### Procedure


## Results



# Model

## Baseline Curiosity Policy

## Antagonistic Curiosity Policy

## Results

We first examine children's choice of drop objects and target objects to see if children had any preference for particular objects.

```{r drop-choice, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
ch_cond <- hum %>% 
  group_by(StimSet, DropChoice) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) 

ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:19) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed')
```

```{r target-hit, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
hum$Target = hum$DropLocation
ch_cond <- hum %>% 
  filter(Target!="outside") %>%
  group_by(StimSet, Target) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) 

ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes, "space"))
ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:20) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Target Object Choice") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed')
```

```{r target-space, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}

hum$TargetSpace = ifelse(hum$DropLocation=="space", hum$WhichSpace, hum$DropLocation)

ch_cond <- hum %>% 
  filter(is.element(TargetSpace, shapes)) %>%
  group_by(StimSet, TargetSpace) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) 

ch_cond$TargetSpace <- factor(ch_cond$TargetSpace, levels = shapes)
ggplot(ch_cond, aes(x=StimSet, y=freq, shape=TargetSpace, color=TargetSpace)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:19) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Target Location Choice") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed')
```

## Comparison with Children



# Discussion 



# Acknowledgements

This work was funded by HAI seed grant #. 
We thank X and Y for helpful comments.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
